Generalized Tractability

### 2023-04-01 GeneralizedTractability_230310.tex

The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying
\[
\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon,
\]
where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL(u_i) \ip[\cf_d]{f}{u_i},
\]
and the complexity of our linear problem is
\begin{equation}\label{eq:comp_def}
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
\end{equation}
The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to identify equivalent conditions in terms of the singular values that are easier to verify than dealing with the definition in \eqref{eq:comp_def}.

>>>>

The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying
\[
\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon,
\]
where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL(u_i) \ip[\cf_d]{f}{u_i},
\]
and the complexity of our linear problem is
\begin{equation}\label{eq:comp_def}
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
\end{equation}

By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity.  This assumes that the Hilbert spaces are defined in such a way that $\lambda_{j,\cdot}$ is non-decreasing, although this assumption is not needed for our results.

The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to bound the complexity in terms of a simple function of $\varepsilon$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
